### 2016-04-22 src/3_TimeSeries.tex
agregando def de RW and ARIMA

%\section{Vector Autoregressive Models}\label{sec:varvec}
\section{Multivariate Time Series modelling}

>>>>

\section{Univariate Time Series modeling}

The random walk model, despite its simplicity is still difficult to outperform for standard econometric forecasting models \cite{lo2011} despite its simplicity. The random walk model is defined as:

\begin{equation}
\mathbf{y}_t = \mathbf{y}_{t-1} + \epsilon_{t}
\label{rwmodel}
\end{equation}

The naive forecast of the time series difference $\hat{\mathbf{y}}_{t+1}$ for the random walk model is defined as:
\begin{equation}
\hat{\mathbf{y}}_{t+1} = \mathbf{y}_t + \hat{\epsilon}_{t+1} 
\end{equation}
\noindent where  $\hat{\epsilon}_{t+1} = \epsilon_{t}$.

On the other hand, ARIMA is widely used to forecast returns in finance \cite{tsay2005}. A process can be modelled as an ARIMA$(p,d,q)$ model if $\mathbf{x}_t=\Delta^d \mathbf{y}_t $, i.e after differencing $d$ times the time series $\mathbf{y}_t$,  we get an ARMA$(p,q)$. An ARMA$(p,q)$ model is the following:

\begin{equation}
\mathbf{x}_t = \sum_{i=1}^p \phi_i \mathbf{x}_{t-i}  +  \sum_{j=1}^q \theta_j \epsilon_{t-j}  
\end{equation}
\noindent with coefficients $\phi_p \neq 0$, $\theta_q \neq 0$ and $\sigma_{\epsilon}^2 > 0$.

\section{Multivariate Time Series modelling}
